Digital economy in the UK: an evolutionary story

### 2023-03-21 presentations/web_diffusion.Rmd
paper first draft

---
title: 'Digital economy in the UK: an evolutionary story'
# date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
author: |
  |
  | Emmanouil Tranos
  |
  | <small>University of Bristol, Alan Turing Institute</small>
  | <small>e.tranos@bristol.ac.uk, [\@EmmanouilTranos](https://twitter.com/EmmanouilTranos), [etranos.info](https://etranos.info/)</small>
output: 
  revealjs::revealjs_presentation:
    theme: simple
    self_contained: true
    reveal_options:
      width: 1150
      height: 720
bibliography: mybibfile.bib
biblio-style: "apalike"
css: style.css
---

@@

## Contents
<br>
<div style="margin-left: 50px !important; text-align:left !important">
- Introduction
- Web data
- Spatial analysis
- S-shaped diffusion curves
- Conclusions
<br>
<br>
[etranos.info/post/gceg2022](https://etranos.info/post/gceg2022/)
</div>

@@

- A **hierarchy effect**: from main centers to secondary ones -- central places

- A **neighborhood effect**: diffusion proceeds outwards from innovation centers, 
first "hitting" nearby rather than far-away locations [@grubler1990rise]

@hagerstrand1965monte: from innovative centers (core) through a
hierarchy of subcenters, to the periphery

@@

> Because new digital activities are rarely---if
ever---captured in official state data, researchers must rely on
information gathered from alternative sources [@zook2022mapping].

@@

## Web data: The Internet Archive
- The largest archive of webpages in the world
- 273 billion webpages from over 361 million websites, 15 petabytes of storage (1996 -)
- A web crawler starts with a list of URLs (a seed list) to crawl and downloads a copy of their content
- Using the hyperlinks included in the crawled URLs, new URLs are identified and crawled (snowball sampling)
- Time-stamp

## Web data: The Internet Archive
![](C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/figure/Picture1.png){width=70%}

## Web data: The Internet Archive
![](C:/Users/nw19521/OneDrive - University of Bristol/projects/archive/nuts/figure/Picture2.png){width=70%}

## Our web data
- JISC UK Web Domain Dataset: all archived webpages from the .uk domain 1996-2012

@@

<!-- <small></small> -->
20080509162138/http://www.website1.co.uk/contact_us IG8 8HD

@@

    <small>- http://www.website1.co.uk/webpage1 and</small>

    <small>- http://www.website1.co.uk/webpage2 are part of the</small>

    <small>- http://www.website1.co.uk</small>

@@

# unique postcodes per website f table
f.websites.pc <- DescTools::Freq(all2000$V1, breaks = c(0, 1,2, 10,100,1000,10000,100000), ord = "desc")
f.websites.pc$level <- factor(f.websites.pc$level, levels = c("[0,1]","(1,2]", "(2,10]", "(10,100]",
                                                              "(100,1e+03]", "(1e+03,1e+04]",
                                                              "(1e+04,1e+05]"))
levels(f.websites.pc$level) <- c("(0,1]","(1,2]", "(2,10]", "(10,100]", "(100,1000]", "(1000,10000]", "(10000,100000]")
kable(f.websites.pc,
      format = "html",
      digits = 3,
      format.args = list(big.mark = ",")) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```
<br>

@@

## Directory website with a lot of postcodes
![](C:/Users/nw19521/OneDrive - University of Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

## Website with a unique postcode in London
![](C:/Users/nw19521/OneDrive - University of Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

@@

---

@@

---

```{r heatmaps_log, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

@@

Two scales:

- Output areas (c. 200,000)

- Local authorities (c. 400)

---

@@

---

```{r moransi_oa, results='asis'}
path.in <- paste0(path, "/outputs/morani_oa.csv")
# read.csv(path.in) %>% dplyr::select(year, morani) %>% 
#   rename('Moran\'s I' = morani,
#          Year = year) %>% 
#   arrange(Year) %>% 
#   kable(digits = 3, 
#         label = "Moran\'s I per year, Output Areas") %>% 
#     kable_classic(full_width = F, html_font = "Cambria")

@@

---

```{r lisa_oa, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/")

@@

<div style="margin-left: 50px !important; text-align:left !important">
$Place$:

@@

$i$: Output Areas *or* Local Authorities
</div>

@@

---

```{r b_London_oa, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_london_oa.png")
knitr::include_graphics(path.image)
```

---

@@

---

```{r b_city_oa, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_city_oa.png")
knitr::include_graphics(path.image)
```

---

@@

---

```{r b_centre_oa, message=FALSE, out.height= "60%", out.width="60%"}
#fig.height=4, fig.width=4, 
path.image <- paste0(path, "/outputs/b_dist_centre_oa.png")
knitr::include_graphics(path.image)
```

---

```{r b_centre_la, message=FALSE, out.height= "60%", out.width="60%"}
path.image <- paste0(path, "/outputs/b_dist_centre_la.png")
knitr::include_graphics(path.image)
```

```{r r_squared, eval=F, results='asis'}
# This is for the RSquared of the different website density regressions.
# The RSquared does not drop much hence it is not worth reporting.

@@

read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>% 
  ggplot(aes(x=year)) +
  geom_line(aes(y=London, color = "OA to London"), size=1) +
  geom_line(aes(y=cities, color = "OA to nearest city"), size=1) +
  geom_line(aes(y=retail, color = "OA to nearest retail centre"), size=1) +

@@

  scale_color_discrete(name = "Website density regressions") +
  scale_linetype_manual(name = "Website density regressions") +
  theme_minimal()

  scale_color_manual(values = c("red", "blue", "green"))

read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>% 
  pivot_longer(names_to = "destinations",
               values_to = "Rsquared",
               cols = 2:7) %>% 
  arrange(destinations, year) %>% 
  ggplot(aes(x=year)) +
  geom_line(aes(y=Rsquared, group=destinations, colour=destinations)) +
  geom_textline(aes(y=Rsquared, group=destinations, colour=destinations, 
                    label=destinations),
                hjust = 1) +
  theme(legend.position = "none") +
  theme_minimal()

@@

---

```{r gini_oa, results='asis'}
path.in <- paste0(path, "/outputs/gini_oa.csv")

@@

```{r Darlington, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000005.png")
knitr::include_graphics(path.image)
```

---

```{r Nottingham, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000018.png")
knitr::include_graphics(path.image)
```

---

```{r Reading, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000038.png")
knitr::include_graphics(path.image)
```

---

```{r City_of_London, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E09000001.png")
knitr::include_graphics(path.image)
```

---

@@

```{r Middlesbrough, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000002.png")
knitr::include_graphics(path.image)
```

---

```{r Leicester, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000016.png")
knitr::include_graphics(path.image)
```

---

```{r Bristol, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000023.png")
knitr::include_graphics(path.image)
```

---

```{r Plymouth, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E06000026.png")
knitr::include_graphics(path.image)
```

---

```{r Liverpool, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E08000012.png")
knitr::include_graphics(path.image)
```

---

```{r Hackney, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_E09000012.png")
knitr::include_graphics(path.image)
```

---

```{r Edinburgh, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/lad_S12000036.png")
knitr::include_graphics(path.image)
```

@@

- Expand our definition of web to websites with # of postcodes > 1

>>>>

---
title: 'Digital economy in the UK: an evolutionary story'
# date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
author: |
  |
  | Emmanouil Tranos
  |
  | <small>University of Bristol, Alan Turing Institute</small>
  | <small>e.tranos@bristol.ac.uk, [\@EmmanouilTranos](https://twitter.com/EmmanouilTranos), [etranos.info](https://etranos.info/)</small>
output: 
  revealjs::revealjs_presentation:
    theme: simple
    self_contained: true
    reveal_options:
      width: 1150
      height: 720
bibliography: mybibfile.bib
biblio-style: "apalike"
css: style.css
editor_options: 
  markdown: 
    wrap: 72
---

@@

## Contents

::: {style="margin-left: 50px !important; text-align:left !important"}
-   Introduction
-   Web data
-   Spatial analysis
-   S-shaped diffusion curves
-   Conclusions <br> <br>
    [etranos.info/post/gceg2022](https://etranos.info/post/gceg2022/)
:::

@@

-   A **hierarchy effect**: from main centres to secondary ones --
    central places

-   A **neighborhood effect**: diffusion proceeds outwards from
    innovation centres, first "hitting" nearby rather than far-away
    locations [@grubler1990rise]

@hagerstrand1965monte: from innovative centres (core) through a
hierarchy of sub-centres, to the periphery

@@

> Because new digital activities are rarely---if ever---captured in
> official state data, researchers must rely on information gathered
> from alternative sources [@zook2022mapping].

@@

## Web data: The Internet Archive

-   The largest archive of webpages in the world
-   273 billion webpages from over 361 million websites, 15 petabytes of
    storage (1996 -)
-   A web crawler starts with a list of URLs (a seed list) to crawl and
    downloads a copy of their content
-   Using the hyperlinks included in the crawled URLs, new URLs are
    identified and crawled (snowball sampling)
-   Time-stamp

## Web data: The Internet Archive

![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture1.png){width="70%"}

## Web data: The Internet Archive

![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture2.png){width="70%"}

-   JISC UK Web Domain Dataset: all archived webpages from the .uk
    domain 1996-2012

@@

<!-- <small></small> -->

20080509162138/<http://www.website1.co.uk/contact_us> IG8 8HD

@@

    <small>- <http://www.website1.co.uk/webpage1> and</small>

    <small>- <http://www.website1.co.uk/webpage2> are part of
    the</small>

    <small>- <http://www.website1.co.uk></small>

@@

# unique postcodes per website f table
f.websites.pc <- DescTools::Freq(all2000$V1, breaks = c(0, 1,2, 10,100,1000,10000,100000), ord = "desc")
f.websites.pc$level <- factor(f.websites.pc$level, levels = c("[0,1]","(1,2]", "(2,10]", "(10,100]",
                                                              "(100,1e+03]", "(1e+03,1e+04]",
                                                              "(1e+04,1e+05]"))
levels(f.websites.pc$level) <- c("(0,1]","(1,2]", "(2,10]", "(10,100]", "(100,1000]", "(1000,10000]", "(10000,100000]")
kable(f.websites.pc,
      format = "html",
      digits = 3,
      format.args = list(big.mark = ",")) %>% 
  kable_classic(full_width = F, html_font = "Cambria")
```

@@

## Directory website with a lot of postcodes

![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

## Website with a unique postcode in London

![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

@@

------------------------------------------------------------------------

@@

<!-- ------------------------------------------------------------------------ -->

```{r eval = F, heatmaps_log, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

@@

@@

-   Websites per firm in Local authorities (c. 400)

<!-- ------------------------------------------------------------------------ -->

```{r, eval=FALSE, moransi_oa, results='asis'}
path.in <- paste0(path, "/outputs/morani_oa.csv")
# read.csv(path.in) %>% dplyr::select(year, morani) %>% 
#   rename('Moran\'s I' = morani,
#          Year = year) %>% 
#   arrange(Year) %>% 
#   kable(digits = 3, 
#         label = "Moran\'s I per year, Output Areas") %>% 
#     kable_classic(full_width = F, html_font = "Cambria")

@@

<!-- ------------------------------------------------------------------------ -->

```{r lisa_oa, eval=FALSE,results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/")

@@

::: {style="margin-left: 50px !important; text-align:left !important"}
$Place$:

@@

-   $Website\,Density_{i}$: Websites per firm in a Local Authority $i$
:::

@@

<!-- ------------------------------------------------------------------------ -->

```{r b_London_oa, eval=F, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_london_oa.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

@@

<!-- ------------------------------------------------------------------------ -->

```{r b_city_oa, eval = F, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_city_oa.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

@@

<!-- ------------------------------------------------------------------------ -->

```{r b_centre_oa, eval = F, message=FALSE, out.height= "60%", out.width="60%"}
#fig.height=4, fig.width=4, 
path.image <- paste0(path, "/outputs/b_dist_centre_oa.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r b_centre_la, message=FALSE}
#, out.height= "60%", out.width="60%"
path.image <- paste0(path, "/outputs/b_dist_centre_la.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r r_squared, eval=T, results='asis'}
# This is for the RSquared of the different website density regressions.
# The RSquared does not drop much hence it is not worth reporting.

@@

read.csv(path.in2) %>% #left_join(read.csv(path.in2)) %>% 
  ggplot(aes(x=year)) +
  # geom_line(aes(y=London, color = "OA to London"), size=1) +
  # geom_line(aes(y=cities, color = "OA to nearest city"), size=1) +
  # geom_line(aes(y=retail, color = "OA to nearest retail centre"), size=1) +

@@

  scale_color_discrete(name = "R-squared for regression:") +
  scale_linetype_manual(name = "Website density regressions") +
  ylab("R-squared") + 
  ggtitle("Website density regressions") +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5))

  # scale_color_manual(values = c("red", "blue", "green"))

# read.csv(path.in2) #%>% left_join(read.csv(path.in2)) %>% 
#   pivot_longer(names_to = "destinations",
#                values_to = "Rsquared",
#                cols = 2:7) %>% 
#   arrange(destinations, year) %>% 
#   ggplot(aes(x=year)) +
#   geom_line(aes(y=Rsquared, group=destinations, colour=destinations)) +
#   geom_textline(aes(y=Rsquared, group=destinations, colour=destinations, 
#                     label=destinations),
#                 hjust = 1) +
#   theme(legend.position = "none") +
#   theme_minimal()

@@

<!-- ------------------------------------------------------------------------ -->

```{r gini_oa, eval=F, results='asis'}
path.in <- paste0(path, "/outputs/gini_oa.csv")

@@

```{r Darlington, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000005.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r Nottingham, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000018.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r Reading, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000038.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r City_of_London, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E09000001.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

@@

```{r Middlesbrough, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000002.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r Leicester, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000016.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r Bristol, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000023.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r Plymouth, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000026.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r Liverpool, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E08000012.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r Hackney, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E09000012.png")
knitr::include_graphics(path.image)
```

------------------------------------------------------------------------

```{r Edinburgh, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_S12000036.png")
knitr::include_graphics(path.image)
```

@@

-   Expand our definition of web to websites with \# of postcodes \> 1
